Investigating soundscapes perception through acoustic scenes simulation

### 2018-09-04 lafaySimulatedScenePerception.tex
fixing typo

On the contrary, the fact that we observe for the non-ideal scenes both significant correlations for $L_m$ and $L(E)_m$ and no correlation for $L_m-L_b$ and $L(E)_m$ - $L(E)_b$, shows that it is indeed the absolute level that matters for non ideal environments.

>>>>

On the contrary, the fact that we observe for the non-ideal scenes both significant correlations for $L_m$ and $L(E)_m$ and no correlation for $L_m-L_b$ and $L(E)_m$ - $L(E)_b$, shows that it is indeed the absolute level that matters for non-ideal environments.
